Fractional Types

### 2013-02-06 frac.tex
added relational semantics for the interpreter

@@

As hinted to in the first section, the semantics of fractional types introduces
a form of non-determinism in the sense that there could zero, one, or several
values that satisfy the constraints imposed by fractional values. To model
such non-determinism, we specify the semantics using \emph{relations}. In
other words, the results of {{evalF c v}} or {{evalB c v}} are no longer
guaranteed to be a single value: they could be \emph{sets} of values.

>>>>

%subcode{proof} include main
%@ ~
%@@ (left v) swap+ (right v)
%
%@ ~
%@@ (right v) swap+ (left v)
%----
%@ ~
%@@ (left v) assocl+ (left (left v))
%
%@ ~
%@@ (right (left v)) assocl+ (left (right v))
%
%@ ~
%@@ (right (right v)) assocl+ (right v)
%----
%@ ~
%@@ (left (left v)) assocr+ (left v)
%
%@ ~
%@@ (left (right v)) assocr+ (right (left v))
%
%@ ~
%@@ (right v) assocr+ (right (right v))
%----
%@ ~
%@@ ((), v) unite v
%
%@ ~
%@@ v uniti ((), v)
%----
%@ ~
%@@ (v1, v2) swap* (v2, v1)
%----
%@ ~
%@@ (v1, (v2, v3)) assocl* ((v1, v2), v3)
%
%@ ~
%@@ ((v1, v2), v3) assocr* (v1, (v2, v3))
%----
%@ ~
%@@ (left v1, v3) dist (left (v1, v3))
%
%@ ~
%@@ (right v2, v3) dist (right (v2, v3))
%----
%@ ~
%@@ (left (v1, v3)) factor (left v1, v3)
%
%@ ~
%@@ (right (v2, v3)) factor (right v2, v3)
%----
%@ ~
%@@ v id v
%
%@ v' c v
%@@ v (sym c) v'
%----
%@ v1 c1 v2
%@ v2 c2 v3
%@@ v1 (c1(;)c2) v3
%
%@ v c1 v'
%@@ (left v) (c1 (+) c2) (left v')
%
%@ v c2 v'
%@@ (right v) (c1 (+) c2) (right v')
%----
%@ v1 c1 v1'
%@ v2 c2 v2'
%@@ (v1, v2) (c1 (*) c2) (v1', v2')
%----
%@ v in [[b]]
%@@ () ~eta*_b (1/v,v)
%
%@ ~
%@@ (1/v,v) ~eps*_b ()

@@

As hinted to in the first section, the semantics of fractional types introduces
a form of non-determinism in the sense that there could be zero, one, or several
values that satisfy the constraints imposed by fractional values. To model
such non-determinism, we specify the semantics using \emph{relations}. In
other words, the results of {{evalF c v}} or {{evalB c v}} are no longer
guaranteed to be a single value: they could be \emph{sets} of values.
